---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Michael Palazzolo"
date: "8/29/2019"
output: 
  html_document: 
    fig_width: 5
    highlight: tango
    theme: journal
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Rows: 1846 \
Columns: 3 \
Variables: dataset, x, y

### Exercise 2


Plot of the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plot of Star data set:

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation coefficnet for Star data set:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```
This r value of the star data set is very similar to the r value of the dino dataset, but there is a weaker correlation in the negative direction in the star data set.

### Exercise 4

Plot of circle data set:

```{r}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation coefficient of circle data set:

```{r}
dino_data %>%
  summarize(r = cor(x, y))
```
The r value of the circle data set is higher in the negative direction. This difference is not much, but the r value of circle has a stronger negative correlation than the dino data set. 

### Exercise 5

Plots of all of the data sets:

```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```

The color = dataset made each plot a different color, so that you can tell the different plots by color. The ncol = 3 made three columns of plots that were shown in the output. The number of rows depneded on how many plots there were, but there would be only 3 columns. The theme comman made it so that there was no legend showing which plots go with which color.

Correlation coefficients for all of the data sets:

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x,y)) %>%
  print(13)
```